Interval Probability for Fuzzy Quantum Theories

### 2016-06-14 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} Add a comment about continuity...

>>>>

\yutsung{About continuity, one of the confusion comes from the subtle
correspondence between the measurement processes and observables.
Consider the following observables and their measurement processes:
\begin{itemize}
\item The observable operator~$\mathbf{O}_{x}=\proj{1}+x\proj{-1}$. Except
$x=1$, the measurement process for $\mathbf{O}_{x}$ is ${\cal O}_{x}$:
\begin{enumerate}
\item With probability~$\mu_{\phi}\left(\proj{1}\right)$, return the measurement
result~$1$ with the post-measurement state~$\ket{1}$;
\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
result~$0$ with the post-measurement state~$\ket{0}$;
\item With probability~$\mu_{\phi}\left(\proj{-1}\right)$, return the
measurement result~$x$ with the post-measurement state~$\ket{-1}$.
\end{enumerate}
\item The observable operator~$\mathbf{J}_{z}^{2}=\proj{1}+\proj{-1}$,
and its measurement process~${\cal J}_{z}^{2}$:
\begin{enumerate}
\item With probability~$\mu_{\phi}\left(\proj{1}+\proj{-1}\right)$, return
the measurement result~$1$ with the post-measurement state~$\ket{1}\ip{1}{\phi}+\ket{-1}\ip{-1}{\phi}$;
\item With probability~$\mu_{\phi}\left(\proj{0}\right)$, return the measurement
result~$0$ with the post-measurement state~$\ket{0}$.
\end{enumerate}
\end{itemize}
As an operator, it is clear that $\lim_{x\rightarrow1}\mathbf{O}_{x}=\mathbf{J}_{z}^{2}$,
and we should have $\lim_{x\rightarrow1}{\cal O}_{x}={\cal O}_{1}$
for the measurement process. However, it is not obvious why ${\cal O}_{1}={\cal J}_{z}^{2}$.
Although they have the same probability for the measurement results,
but their post-measurement states are different. This might be a defect
of representing a measurement process as an observable. As $\mathbf{O}_{1}=\mathbf{J}_{z}^{2}$,
there is no observable corresponding to the measurement process~${\cal O}_{1}$.}
